*flippant* -- An R package for the automated analysis of dithionite scramblase

### 2016-03-20 inst/manuscript/manuscript.rmd
Adapt to the change of fitting routine in flippant;

Results from *flippant*-driven analysis track prior manual analysis well. 
Deviations observed may stem from algorithmic differences such as the fitting 
routine used (*flippant* uses the Nash variant of the Marquardt 
nonlinear least squares algorithm as implemented by @nash_nlmrt:_2014) and 
general handling of significant digits and rounding.

>>>>

Results from *flippant*-driven analysis track prior manual analysis well. 
Deviations observed may stem from algorithmic differences such as the fitting 
routine used (*flippant* uses the the Marquardt nonlinear least squares
algorithm as implemented by @elzhov_minpack.lm:_2015) and 
general handling of significant digits and rounding.
